---
title: "Prediction of Seizures in Children after Traumatic Brain Injury"
date: "March 27, 2017"
output: 
  ioslides_presentation:
    keep_md: true
htmlwidgets: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(plotly)
data("presidents")
ts <- window(presidents, start=c(1960, 1), end=c(1974, 4))
```

## Pediatric Traumatic Brain Injury (TBI)

- is common
- is the leading cause of mortality and acquired disability in children

## Seizures after TBI

- brain injury lowers seizure threshold
- seizures can cause additional brain injury

## Seizure Prediction

- prediction of seizure likelihood would inform providers which patients are at risk
- they can then attempt to limit seizures with medications

## Example

- A 3 yo child has TBI from a fall
- Subdural hemorrhage is not present on the CT scan

```{r example, echo = FALSE, warning = FALSE, message = FALSE}
### input parameters
age <- 3 ### age in years
abuse <- 0 ### injury was not inflicted
sdh <- 0 ### no subdural hemorrhage


odds <- exp(-0.82483 + 
                           (-0.00608*12)*age + 
                           0.91957*abuse + 
                           0.71204*sdh + 
                           (-0.00267*12*age*abuse) +
                           (-0.00749*12*age*sdh) +
                           (-0.36054*abuse*sdh))
               
prob <- paste0(round(100*(odds/(1 + odds)),1), "%")


### knit and then use the publish button to send to Rpubs
### vs push to github pages
```
<br>

- Seizure Risk: `r prob`
<br>
<br>

- https://pedstbi.shinyapps.io/seizure_prediction/

